The limits of self commitment and private paternalism \thanks{}

### 2022-03-24 OA.tex
_learning over time & fix choose_wrong & fix distcomp_

@@

\begin{figure}[H]
        \caption{Repeat purchase before 30/60 days}
    \label{reincidence_before}
    \begin{center}
        \centering
        \includegraphics[width=0.50\textwidth]{Figuras/re_te_earlydays.pdf}
    \end{center}
     \scriptsize This figure shows the estimated treatment effect of repeat purchase before 30 \& 60 days.
     %\textit{Do file: }  \texttt{re\_te\_earlydays.do}
\end{figure}

@@

\begin{comment}
\begin{figure}[H]
    \caption{Heterogeneous Treatment Effect: Promise-forcing contract}
    \label{heterogeneous_te_3}
    \begin{center}
    \begin{subfigure}{0.4\textwidth}
        \caption{Financial cost}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_3.pdf}
    \end{subfigure}
    \begin{subfigure}{0.4\textwidth}
        \caption*{}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_3.pdf}
    \end{subfigure}

    \begin{subfigure}{0.4\textwidth}
        \caption{Losing Pawn}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_3.pdf}
    \end{subfigure}
    \begin{subfigure}{0.4\textwidth}
        \caption*{}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_3.pdf}
    \end{subfigure}
    \end{center}
     \scriptsize
      %\footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
\end{figure}
\end{comment}

\begin{comment}

\begin{figure}[H]
    \caption{Heterogeneous Treatment Effect - Choice/Fee}
    \label{heterogeneous_te_4}
    \begin{center}
    \begin{subfigure}{0.4\textwidth}
        \caption{Financial cost}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_4.pdf}
    \end{subfigure}
    \begin{subfigure}{0.4\textwidth}
        \caption*{}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_4.pdf}
    \end{subfigure}

    \begin{subfigure}{0.4\textwidth}
        \caption{Losing Pawn}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_4.pdf}
    \end{subfigure}
    \begin{subfigure}{0.4\textwidth}
        \caption*{}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_4.pdf}
    \end{subfigure}
    \end{center}
     \footnotesize \textit{Notes: } The distribution plots the FC treatment effect for the interval $[\mu-2\sigma,\mu+2\sigma]$ to ignore the outliers.
      \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
\end{figure}

\begin{figure}[H]
    \caption{Heterogeneous Treatment Effect - Choice/Promise}
    \label{heterogeneous_te_5}
    \begin{center}
    \begin{subfigure}{0.4\textwidth}
        \caption{Financial cost}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_5.pdf}
    \end{subfigure}
    \begin{subfigure}{0.4\textwidth}
        \caption*{}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_5.pdf}
    \end{subfigure}
    \begin{subfigure}{0.4\textwidth}
        \caption{Losing Pawn}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_5.pdf}
    \end{subfigure}
    \begin{subfigure}{0.4\textwidth}
        \caption*{}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_5.pdf}
    \end{subfigure}
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
\end{figure}

\end{comment}

@@

\subsection{New results}
\begin{figure}[H]
        \caption{Financial cost for different discount rates}
    \label{fc_discount_rates}
    \begin{center}
        \centering
        \includegraphics[width=0.55\textwidth]{Figuras/discount_effect.pdf}
    \end{center}
     \scriptsize This Figure estimates the treatment effect on financial cost with different discount rates.  
     %\textit{Do file: }  \texttt{discounted\_noeffect.do}
\end{figure}

@@

\scriptsize {
\noindent This Figure shows the treatment effects for the main outcomes when pooling all arms in the same regression.
}

\begin{figure}[H]
        \caption{Treatment effect decomposition of the Financial Cost }
    \label{reg_int_pro_2}
    \begin{center}
        \centering
        \includegraphics[width=0.60\textwidth]{Figuras/int_te_pro_2.pdf}
    \end{center}
     \scriptsize This Figure is a "close-up" for the estimates found in Figure \ref{fc_pro2} - Panel (a). It shows the treatment effects on payed \& incurred interest, the former defined as the actual interest payed, and the latter is the sum of all potential interests (for those pawns that were lost we calculate the interest generated until day 230). In the right axis we show the treatment effect on the payed fees. Finally, we analyze this effect for the subsamples that recovers or loses the pawn.
     %\textit{Do file: }  \texttt{reg_\int.do}
\end{figure}

@@

\begin{figure}[H]
    \caption{Histogram of payments}
    \label{hist_payments}
    \begin{center}
    \begin{subfigure}{0.31\textwidth}
        \caption{Status-quo}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_payments_sq.pdf}
    \end{subfigure}
    \begin{subfigure}{0.31\textwidth}
        \caption{Forced commitment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_payments_fc.pdf}
    \end{subfigure}
    \begin{subfigure}{0.31\textwidth}
        \caption{Choice commitment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_payments_cc.pdf}
    \end{subfigure}    
        \begin{subfigure}{0.31\textwidth}
        \caption{Forced soft}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_payments_fs.pdf}
    \end{subfigure}
    \begin{subfigure}{0.31\textwidth}
        \caption{Choice soft}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_payments_cs.pdf}
    \end{subfigure} 
    \end{center}
     \scriptsize
      %\footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
\end{figure}

\begin{figure}[H]
        \caption{Survival graphs}
    \label{survival_graph}
    \begin{center}
   \begin{subfigure}{0.45\textwidth}
        \caption{Closed contracts}
        \centering
        \includegraphics[width=\textwidth]{Figuras/survival_graph_ended.pdf}
    \end{subfigure} 
       \begin{subfigure}{0.45\textwidth}
        \caption{Recovery}
        \centering
        \includegraphics[width=\textwidth]{Figuras/survival_graph_unpledge.pdf}
    \end{subfigure} 
    \end{center}
     \scriptsize  This Figure shows the accumulated percentage of recovery in time by treatment arm. 
     %\textit{Do file: }  \texttt{survival\_graph.do}
\end{figure}

@@

\begin{comment}
\begin{figure}[H]
        \caption{Percentage of payments}
    \label{perc_payments}
    \begin{center}
    \begin{subfigure}{.31\textwidth}
    \caption{Control}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_1.pdf}
    \end{subfigure}
    \begin{subfigure}{.31\textwidth}
    \caption{Forcing - fee}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_2.pdf}
    \end{subfigure}   
     \begin{subfigure}{.31\textwidth}
    \caption{Forcing - promise}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_3.pdf}
    \end{subfigure}  
     \begin{subfigure}{.31\textwidth}
    \caption{Choice - fee}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_4.pdf}
    \end{subfigure}  
     \begin{subfigure}{.31\textwidth}
    \caption{Choice - fee - SQ}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_6.pdf}
    \end{subfigure}    
     \begin{subfigure}{.31\textwidth}
    \caption{Choice - fee - NSQ}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_7.pdf}
    \end{subfigure}    
     \begin{subfigure}{.31\textwidth}
    \caption{Choice - promise}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_5.pdf}
    \end{subfigure}  
     \begin{subfigure}{.31\textwidth}
    \caption{Choice - promise - SQ}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_8.pdf}
    \end{subfigure}    
     \begin{subfigure}{.31\textwidth}
    \caption{Choice - promise - NSQ}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_9.pdf}    
    \end{subfigure}        
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
\end{figure}

\begin{figure}[H]
        \caption{Percentage of payment conditional on positive payment and Losing Pawn}
    \label{perc_payments_conditional}
    \begin{center}
    \begin{subfigure}{.31\textwidth}
    \caption{Control}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_1.pdf}
    \end{subfigure}
    \begin{subfigure}{.31\textwidth}
    \caption{Forcing - fee}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_2.pdf}
    \end{subfigure}   
     \begin{subfigure}{.31\textwidth}
    \caption{Forcing - promise}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_3.pdf}
    \end{subfigure}  
     \begin{subfigure}{.31\textwidth}
    \caption{Choice - fee}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_4.pdf}
    \end{subfigure}  
     \begin{subfigure}{.31\textwidth}
    \caption{Choice - fee - SQ}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_6.pdf}
    \end{subfigure}    
     \begin{subfigure}{.31\textwidth}
    \caption{Choice - fee - NSQ}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_7.pdf}
    \end{subfigure}    
     \begin{subfigure}{.31\textwidth}
    \caption{Choice - promise}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_5.pdf}
    \end{subfigure}  
     \begin{subfigure}{.31\textwidth}
    \caption{Choice - promise - SQ}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_8.pdf}
    \end{subfigure}    
     \begin{subfigure}{.31\textwidth}
    \caption{Choice - promise - NSQ}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_9.pdf}    
    \end{subfigure}        
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
\end{figure}
\end{comment}

@@

\begin{comment}

\begin{figure}[H]
        \caption{FC effect for different discount rates}
    \label{oc_hist}
    \begin{center}
        \centering
        \includegraphics[width=0.50\textwidth]{Figuras/discount_effect.pdf}
    \end{center}
    \footnotesize \textit{Notes: } 
     \footnotesize{ \textit{Do file: }  \texttt{discounted\_noeffect.do}}
\end{figure}
\end{comment}

>>>>

\begin{table}[H]
\caption{Effects on several definitions of cost - Soft arms}
\label{table_robustness_fc_soft}
\begin{center}
\scriptsize{\input{./Tables/fc_robustness_soft.tex}}
\end{center}
 \scriptsize

%\textit{Do file: } \texttt{fc\_robustness\_soft.do}
\end{table}

\begin{landscape}

\begin{table}[H]
\caption{Intermediate outcomes - Soft arms}
\label{mechanisms_soft}
\begin{center}
\scriptsize{\input{./Tables/mechanism_soft.tex}}
\end{center}

%\textit{Do file: } \texttt{mechanisms\_soft.do}
\end{table}

\end{landscape}

\cleardoublepage

@@

% \begin{figure}[H]
%         \caption{Repeat purchase before 30/60 days}
%     \label{reincidence_before}
%     \begin{center}
%         \centering
%         \includegraphics[width=0.50\textwidth]{Figuras/re_te_earlydays.pdf}
%     \end{center}
%      \scriptsize This figure shows the estimated treatment effect of repeat purchase before 30 \& 60 days.
%      %\textit{Do file: }  \texttt{re\_te\_earlydays.do}
% \end{figure}

@@

% \begin{figure}[H]
%     \caption{Heterogeneous Treatment Effect: Promise-forcing contract}
%     \label{heterogeneous_te_3}
%     \begin{center}
%     \begin{subfigure}{0.4\textwidth}
%         \caption{Financial cost}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_3.pdf}
%     \end{subfigure}
%     \begin{subfigure}{0.4\textwidth}
%         \caption*{}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_3.pdf}
%     \end{subfigure}

%     \begin{subfigure}{0.4\textwidth}
%         \caption{Losing Pawn}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_3.pdf}
%     \end{subfigure}
%     \begin{subfigure}{0.4\textwidth}
%         \caption*{}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_3.pdf}
%     \end{subfigure}
%     \end{center}
%      \scriptsize
%       %\footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
% \end{figure}

% \begin{figure}[H]
%     \caption{Heterogeneous Treatment Effect - Choice/Fee}
%     \label{heterogeneous_te_4}
%     \begin{center}
%     \begin{subfigure}{0.4\textwidth}
%         \caption{Financial cost}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_4.pdf}
%     \end{subfigure}
%     \begin{subfigure}{0.4\textwidth}
%         \caption*{}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_4.pdf}
%     \end{subfigure}

%     \begin{subfigure}{0.4\textwidth}
%         \caption{Losing Pawn}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_4.pdf}
%     \end{subfigure}
%     \begin{subfigure}{0.4\textwidth}
%         \caption*{}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_4.pdf}
%     \end{subfigure}
%     \end{center}
%      \footnotesize \textit{Notes: } The distribution plots the FC treatment effect for the interval $[\mu-2\sigma,\mu+2\sigma]$ to ignore the outliers.
%       \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
% \end{figure}

% \begin{figure}[H]
%     \caption{Heterogeneous Treatment Effect - Choice/Promise}
%     \label{heterogeneous_te_5}
%     \begin{center}
%     \begin{subfigure}{0.4\textwidth}
%         \caption{Financial cost}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_5.pdf}
%     \end{subfigure}
%     \begin{subfigure}{0.4\textwidth}
%         \caption*{}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_5.pdf}
%     \end{subfigure}
%     \begin{subfigure}{0.4\textwidth}
%         \caption{Losing Pawn}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_5.pdf}
%     \end{subfigure}
%     \begin{subfigure}{0.4\textwidth}
%         \caption*{}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_5.pdf}
%     \end{subfigure}
%     \end{center}
%      \footnotesize \textit{Notes: } 
%       \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
% \end{figure}

@@

\subsection{New results}

@@

% \begin{figure}[H]
%         \caption{Treatment effect decomposition of the Financial Cost }
%     \label{reg_int_pro_2}
%     \begin{center}
%         \centering
%         \includegraphics[width=0.60\textwidth]{Figuras/int_te_pro_2.pdf}
%     \end{center}
%      \scriptsize This Figure is a "close-up" for the estimates found in Figure \ref{fc_pro2} - Panel (a). It shows the treatment effects on payed \& incurred interest, the former defined as the actual interest payed, and the latter is the sum of all potential interests (for those pawns that were lost we calculate the interest generated until day 230). In the right axis we show the treatment effect on the payed fees. Finally, we analyze this effect for the subsamples that recovers or loses the pawn.
%      %\textit{Do file: }  \texttt{reg_\int.do}
% \end{figure}

@@

@@

% \begin{figure}[H]
%         \caption{Percentage of payments}
%     \label{perc_payments}
%     \begin{center}
%     \begin{subfigure}{.31\textwidth}
%     \caption{Control}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_1.pdf}
%     \end{subfigure}
%     \begin{subfigure}{.31\textwidth}
%     \caption{Forcing - fee}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_2.pdf}
%     \end{subfigure}   
%      \begin{subfigure}{.31\textwidth}
%     \caption{Forcing - promise}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_3.pdf}
%     \end{subfigure}  
%      \begin{subfigure}{.31\textwidth}
%     \caption{Choice - fee}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_4.pdf}
%     \end{subfigure}  
%      \begin{subfigure}{.31\textwidth}
%     \caption{Choice - fee - SQ}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_6.pdf}
%     \end{subfigure}    
%      \begin{subfigure}{.31\textwidth}
%     \caption{Choice - fee - NSQ}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_7.pdf}
%     \end{subfigure}    
%      \begin{subfigure}{.31\textwidth}
%     \caption{Choice - promise}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_5.pdf}
%     \end{subfigure}  
%      \begin{subfigure}{.31\textwidth}
%     \caption{Choice - promise - SQ}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_8.pdf}
%     \end{subfigure}    
%      \begin{subfigure}{.31\textwidth}
%     \caption{Choice - promise - NSQ}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_9.pdf}    
%     \end{subfigure}        
%     \end{center}
%      \footnotesize \textit{Notes: } 
%       \footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
% \end{figure}

% \begin{figure}[H]
%         \caption{Percentage of payment conditional on positive payment and Losing Pawn}
%     \label{perc_payments_conditional}
%     \begin{center}
%     \begin{subfigure}{.31\textwidth}
%     \caption{Control}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_1.pdf}
%     \end{subfigure}
%     \begin{subfigure}{.31\textwidth}
%     \caption{Forcing - fee}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_2.pdf}
%     \end{subfigure}   
%      \begin{subfigure}{.31\textwidth}
%     \caption{Forcing - promise}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_3.pdf}
%     \end{subfigure}  
%      \begin{subfigure}{.31\textwidth}
%     \caption{Choice - fee}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_4.pdf}
%     \end{subfigure}  
%      \begin{subfigure}{.31\textwidth}
%     \caption{Choice - fee - SQ}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_6.pdf}
%     \end{subfigure}    
%      \begin{subfigure}{.31\textwidth}
%     \caption{Choice - fee - NSQ}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_7.pdf}
%     \end{subfigure}    
%      \begin{subfigure}{.31\textwidth}
%     \caption{Choice - promise}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_5.pdf}
%     \end{subfigure}  
%      \begin{subfigure}{.31\textwidth}
%     \caption{Choice - promise - SQ}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_8.pdf}
%     \end{subfigure}    
%      \begin{subfigure}{.31\textwidth}
%     \caption{Choice - promise - NSQ}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_9.pdf}    
%     \end{subfigure}        
%     \end{center}
%      \footnotesize \textit{Notes: } 
%       \footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
% \end{figure}

@@

% \begin{figure}[H]
%         \caption{FC effect for different discount rates}
%     \label{oc_hist}
%     \begin{center}
%         \centering
%         \includegraphics[width=0.50\textwidth]{Figuras/discount_effect.pdf}
%     \end{center}
%     \footnotesize \textit{Notes: } 
%      \footnotesize{ \textit{Do file: }  \texttt{discounted\_noeffect.do}}
% \end{figure}
